---
title: "ex16"
author: "Robert A. Stevens"
date: "July 26, 2014"
output: html_document
---

http://learnpythonthehardway.org/book/ex16.html

Exercise 16: Reading and Writing Files

## Python code

**TODO**:  figure out how to do this in RMarkdown

There are actually two things you will see. First the output of your new script:

$ python ex16.py test.txt

```{r, engine='python'}
from sys import argv

script, filename = argv

print "We're going to erase %r." % filename
print "If you don't want that, hit CTRL-C (^C)."
print "If you do want that, hit RETURN."

raw_input("?")

print "Opening the file..."
target = open(filename, 'w')

print "Truncating the file.  Goodbye!"
target.truncate()

print "Now I'm going to ask you for three lines."

line1 = raw_input("line 1: ")
line2 = raw_input("line 2: ")
line3 = raw_input("line 3: ")

print "I'm going to write these to the file."

target.write(line1)
target.write("\n")
target.write(line2)
target.write("\n")
target.write(line3)
target.write("\n")

print "And finally, we close it."
target.close()
```

So that it shows:

We're going to erase 'test.txt'.  
If you don't want that, hit CTRL-C (^C).  
If you do want that, hit RETURN.  
?  
Opening the file...  
Truncating the file.  Goodbye!  
Now I'm going to ask you for three lines.  
line 1:  Mary had a little lamb  
line 2:  It's fleece was white as snow  
line 3:  It was also tasty  
I'm going to write these to the file.  
And finally, we close it.  

## R code

**TODO**:  figure out how to do same/similar in R

In the meantime, substitute the following:

```{r, results="hold", collapse=TRUE}
from sys import argv

script, filename = argv

print "We're going to erase %r." % filename
print "If you don't want that, hit CTRL-C (^C)."
print "If you do want that, hit RETURN."

raw_input("?")

print "Opening the file..."
target = open(filename, 'w')

print "Truncating the file.  Goodbye!"
target.truncate()

print "Now I'm going to ask you for three lines."

line1 = raw_input("line 1: ")
line2 = raw_input("line 2: ")
line3 = raw_input("line 3: ")

print "I'm going to write these to the file."

target.write(line1)
target.write("\n")
target.write(line2)
target.write("\n")
target.write(line3)
target.write("\n")

print "And finally, we close it."
target.close()
```