---
title: "ex15"
author: "Robert A. Stevens"
date: "July 26, 2014"
output: html_document
---

http://learnpythonthehardway.org/book/ex15.html

Exercise 15: Reading Files

## Python code

**TODO**:  figure out how to do this in RMarkdown

I made a file called "ex15_sample.txt" and ran my script.

$ python ex15.py ex15_sample.txt

```{r, engine='python'}
# from sys import argv

# script, filename = argv

filename = "ex15_sample.txt"

txt = open(filename)

print "Here's your file %r:" % filename
print txt.read()

print "Type the filename again:"
# file_again = raw_input("> ")
file_again = filename

txt_again = open(file_again)

print txt_again.read()
```

So that it shows:

Here's your file 'ex15_sample.txt':  
This is stuff I typed into a file.  
It is really cool stuff.  
Lots and lots of fun to have in here.  
  
  
Type the filename again:  
>  ex15_sample.txt  
This is stuff I typed into a file.  
It is really cool stuff.  
Lots and lots of fun to have in here.    

## R code

**TODO**:  figure out how to do same/similar in R

In the meantime, substitute the following:

```{r, results="hold", collapse=TRUE}
filename <- "ex15_sample.txt"
txt <- readLines(filename)
sprintf("Here's your file %s:", filename)
print(txt)
print("Type the filename again:")
file_again <- filename # file_again <- readline("> ")
txt_again <- readLines(file_again)
print(txt_again)
```
