---
title: "ex13"
author: "Robert A. Stevens"
date: "July 26, 2014"
output: html_document
---

http://learnpythonthehardway.org/book/ex13.html

Exercise 13: Parameters, Unpacking, Variables

## Python code

**TODO**:  figure out how to do this in RMarkdown

Run the program like this (and you must pass three command line arguments):

$ python ex13.py first 2nd 3rd

```{r, engine='python'}
from sys import argv

script, first, second, third = argv

print "The script is called:", script
print "Your first variable is:", first
print "Your second variable is:", second
print "Your third variable is:", third
```

```{python}
from sys import argv

script, first, second, third = argv

print "The script is called:", script
print "Your first variable is:", first
print "Your second variable is:", second
print "Your third variable is:", third
```


So that it shows:

> The script is called: ex13.py  
> Your first variable is: first  
> Your second variable is: 2nd  
> Your third variable is: 3rd  

## R code

**TODO**:  figure out how to do same/similar in R

In the meantime, substitute the following:

```{r, results="hold", collapse=TRUE}
# http://adv-r.had.co.nz/Functions.html
f <- function(x) x^2
print("The function is:")
f
print("The function's formals are:")
formals(f)
print("The function's body is:")
body(f)
print("The fuction's environment is:")
environment(f)
```
