---
title: "ex14"
author: "Robert A. Stevens"
date: "July 26, 2014"
output: html_document
---

http://learnpythonthehardway.org/book/ex14.html

Exercise 14: Prompting and Passing

## Python code

**TODO**:  figure out how to do this in RMarkdown

When you run this, remember that you have to give the script your name for the argv arguments.

$ python ex14.py zed

```{r, engine='python'}
from sys import argv

script, user_name = argv
prompt = '> '

print "Hi %s, I'm the %s script." % (user_name, script)
print "I'd like to ask you a few questions."
print "Do you like me %s?" % user_name
likes = raw_input(prompt)

print "Where do you live %s?" % user_name
lives = raw_input(prompt)

print "What kind of computer do you have?"
computer = raw_input(prompt)

print """
Alright, so you said %r about liking me.
You live in %r.  Not sure where that is.
And you have a %r computer.  Nice.
""" % (likes, lives, computer)
```

So that it shows:

Hi zed, I'm the ex14.py script.  
I'd like to ask you a few questions.  
Do you like me zed?  
>  Yes  
Where do you live zed?  
>  San Francisco  
What kind of computer do you have?  
>  Tandy 1000  

Alright, so you said 'Yes' about liking me.  
You live in 'San Francisco'.  Not sure where that is.  
And you have a 'Tandy 1000' computer.  Nice.  

## R code

**TODO**:  figure out how to do same/similar in R

In the meantime, substitute the following:

```{r, results="hold", collapse=TRUE}
script <- "ex14.R"
user_name <- "zed"
prompt <- '> '

sprintf("Hi %s, I'm the %s script.", user_name, script)
sprintf("I'd like to ask you a few questions.")
sprintf("Do you like me %s?", user_name)
(likes <- "Yes") # instead of "likes <- readline(prompt)"

sprintf("Where do you live %s?", user_name)
(lives <- "San Francisco") # instead of "lives <- readline(prompt)"

sprintf("What kind of computer do you have?")
(computer <- "Tandy 1000") # instead of "computer < readline(prompt)"

sprintf("Alright, so you said %s about liking me.", likes)
sprintf("You live in %s.  Not sure where that is.", lives)
sprintf("And you have a %s computer.  Nice.", computer)
```
